Double Trouble: Understanding Sex Differences in Synthetic Lethal interactions in Human Cancers \\~\\ Project Updates

### 2023-07-15 july18meeting_pres2/may30ccgmeeting.tex
updates

	\begin{frame}{Supplementary 2 - Gene Expression Across Tissues}
		content...
	\end{frame}

>>>>

	\begin{frame}{Supplementary 2 - Gene Expression Across Tissues}
		\centering \includegraphics[width=9cm, height=8cm]{all_cancerspairedboxplot_cancertype_0.9_lcal1male.png}
	\end{frame}

	\begin{frame}{Supplementary 2 - Gene Expression Across Tissues}
		\centering \includegraphics[width=9cm, height=8cm]{all_cancerspairedboxplot_cancertype_0.9_lcal1female.png}
	\end{frame}

	\begin{frame}
		content...
	\end{frame}
